### 2016-07-28 Docs/managing_jobs/managingjobs.tex

@@

You can also run \yt\ python scripts in the titan batch queues to do your
visualization.  You need to install \yt\ and all its dependencies
manually somewhere on a {\em Lustre filesystem}---this ensures that the
compute nodes can see it.  A good choice is the project space, since
that has a longer purge window.

Once \yt\ is install by the {\tt install\_script.sh} script, it will
tell you what script to source to define the necessary paths.

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in {\tt
MAESTRO/Util/job\_scripts/titan/} will manage the \yt jobs by calling a
python script for each file that matches a pattern.  Make sure you set
the proper path for the \yt\ {\tt activate} script in {\tt
parallel-yt-new}---this ensures that the paths to the various libraries
are set on the compute nodes.

Note that the actual visualization command itself is launched by
{\tt parallel-yt-new} using the {\tt aprun} command.  This is the
only way to get a job to run on the compute nodes on titan.  But
{\tt aprun} can only launch a single job at a time, so this means
we cannot easily do (trivally) parallel visualization on a node.  For
this reason, running on rhea is preferred.

>>>>

{\color{red} this section needs to be updated.  See the titan section}

@@

You can run \yt\ python scripts in the titan batch queues to do your
visualization.  You need to install \yt\ and all its dependencies
manually somewhere on a {\em Lustre filesystem}---this ensures that the
compute nodes can see it.  A good choice is the project space, since
that has a longer purge window.  The following procedure will setup
the development version of \yt\ (from source)
\begin{itemize}
\item create a directory in your {\tt \$PROJWORK} directory named {\tt yt/}

\item in {\tt yt/}, down load the \yt\ install script:
\begin{verbatim}
wget https://bitbucket.org/yt_analysis/yt/raw/yt/doc/install_script.sh
\end{verbatim}

\item edit the script to use Conda to get the necessary dependencies
and to build \yt\ from source.  This is accomplished by setting the 
following variables near the top of the script:
\begin{verbatim}
INST_CONDA=1
INST_YT_SOURCE=1
\end{verbatim}

\item run the script:
\begin{verbatim}
source install_script.sh
\end{verbatim}
\end{itemize}

When the script is done, you will have a new python installation in a sub-directory
called {\tt yt-conda/} and the script will tell you how to modify your path
in your {\tt .bashrc}

{\bfseries Important: make sure that you are not loading any other
  python environments in your {\tt .bashrc}, e.g., via modules.}

To test thing out, start up the python shell, and try doing {\tt
  import yt}.  If there are no errors, then you are good.

The python code {\tt vol.py} and submission script {\tt
  yt-vis-titan.run} in {\tt MAESTRO/Util/job\_scripts/titan/vis/} show
how to do a simple visualization in the batch queue using yt.  Note
that {\tt vol.py} is executable, and that we run it via {\tt aprun} to
ensure that it is launched on the compute node.

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in that
same directorywill manage the \yt jobs by calling a
python script for each file that matches a pattern.  
Note that the actual visualization command itself is launched by
{\tt parallel-yt-new}, again using the {\tt aprun} command.  But
{\tt aprun} can only launch a single job at a time, so this means
we cannot easily do (trivally) parallel visualization on a node.  For
this reason, running on rhea is preferred.
